What is happening on Twitter? Tweet analysis and undergraduate research projects

### 2020-05-27 Rmd/jse-special-issue-2020.Rmd
added tuning plots

We used functions from the `rtweet` R package to parse tweet JSON into a data frame [@]. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.

>>>>

We used functions from the `rtweet` R package to parse tweet JSON into a data frame [@rtweet-package]. 
We then divided tweet text into words with functions from the `tidytext` R package [@tidytext]. We 
discarded commonly used "stop words" and emojis.
